Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-30 doc/main_jfm.tex
update sec 4.2 numbers

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels (b) and (c), the cross and asterisk symbols are numerical results and fit by using solid lines.}
    \label{figure:permeability}
\end{figure}

@@

Data obtained for the above model.
Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 109$ pN nm$^{-1}$ which gives 26.5 kT nm$^{-2}$.
This value is in good agreement with the 60 kT nm$^{-2}$ from experimental measurements.  The calculated permeability was 
$0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ = 
$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. (double check value; too large)
Case 2. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 62$ pN nm$^{-1}$ which gives 15 kT nm$^{-2}$ which is small.
For permeability we get 0.0566 $\mu$m s$^{-1}$ Pa$^{-1}$.

@@

\todo[inline]{If $B$ is the numerically calculated friction coefficient,
then $b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.

If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN
nm$^{-2}$ is the dimensional pressure.}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels (b) and (c), the cross and asterisk symbols are numerical results and fitted by using solid lines.}
    \label{figure:permeability}
\end{figure}

@@

Data obtained for the above model.
Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 179$ pN nm$^{-1}$ which gives 43.6 kT nm$^{-2}$.
This value is in good agreement with the 60 kT nm$^{-2}$ from experimental measurements.  The calculated permeability was 
$0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ = 
$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. %(double check value; too large)
Case 2. 119 particles with diameter 2.5 nm and $L_0 = 218$ nm. This data set gave  $K_A = 160$ pN nm$^{-1}$ which gives 39 kT nm$^{-2}$. For permeability we get 0.0283 $\mu$m s$^{-1}$ Pa$^{-1}$.
Case 3. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 102$ pN nm$^{-1}$ which gives 24.8 kT nm$^{-2}$ which is small.
For permeability we get 0.0566 $\mu$m s$^{-1}$ Pa$^{-1}$.

@@

%\todo[inline]{If $B$ is the numerically calculated friction coefficient,
%then $b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
%
%If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN
%nm$^{-2}$ is the dimensional pressure.}
